Industrial, large-scale model predictive control with structured neural networks

### 2020-09-05 paper.tex
send the draft.

The offline data generation and training times 
to build the NNs show that this large dimensional example
is tractable with the proposed NN approach.
This large example is challenging, 
since on average the QP solver CVXOPT takes 37 seconds
and 57 seconds in the worst-case. In comparison,  
all the NNs execute MPC in about 2 to 6 milliseconds.
As observed from the plot of the transient controller 
performance index, the performance 
degradation by the NNs relative to 
the optimal MPC controller is negligible.
The sampling of the state-space with 
the setpoint and disturbance signals
for one particular operational scenario,
combined with the offset-free NN structure
are key steps for scalability in this example.

>>>>

The offline data generation and training times 
to build the NNs show that this large dimensional example
is tractable with the proposed NN approach.
This large example is challenging, 
since on average the QP solver CVXOPT takes 37 seconds
and 57 seconds in the worst-case. In comparison,  
all the NNs execute MPC in about 2 to 6 milliseconds.
As observed from the plot of the transient controller 
performance index, the performance 
degradation by the NNs relative to 
the optimal MPC controller is negligible.
The sampling of the state-space with 
the setpoint and disturbance signals
for one particular operational scenario,
combined with the offset-free NN structure
are the key steps for scalability in this example.
